Spitzer, Gaia, and the Potential of the Milky Way

### 2013-09-19 text/paper1/ms.tex
typo in email address
clarified figure 3

% affiliations
\altaffiltext{1}{Department of Astronomy, Columbia University, 550 W 120th St., New York, NY 027, USA}
%\altaffiltext{2}{NSF Graduate Fellow}
\altaffiltext{2}{\email{adrn@astro.columia.edu}}

@@

\begin{figure}[h]
\begin{center}
%\includegraphics[width=0.47\textwidth,trim=5 0 0 0, clip]{/Users/adrian/projects/streams/plots/paper1/ps_distance.eps}
\includegraphics[width=0.47\textwidth,trim=5 0 0 0, clip]{/Users/adrian/projects/streams/plots/paper1/ps_distance.pdf}
\caption{Phase space distance ($D_{\rm ps}$) for 10 stars integrated backwards in the correct potential (top) and a potential where $q_z$ is 25\% larger (bottom). The same 10 particles are used in both figures, so the initial conditions are identical. Red (thick, solid line) shows the galactocentric distance of the progenitor (in arbitrary, normalized units) over the integration. Horizontal (dashed) line shows $D_{\rm ps}=\sqrt{2}$.}\label{fig:ps_distance}
\end{center}
\end{figure}

>>>>

% affiliations
\altaffiltext{1}{Department of Astronomy, Columbia University, 550 W 120th St., New York, NY 027, USA}
%\altaffiltext{2}{NSF Graduate Fellow}
\altaffiltext{2}{\email{adrn@astro.columbia.edu}}

@@

\begin{figure}[h]
\begin{center}
%\includegraphics[width=0.47\textwidth,trim=5 0 0 0, clip]{/Users/adrian/projects/streams/plots/paper1/ps_distance.eps}
\includegraphics[width=0.47\textwidth,trim=5 0 0 0, clip]{/Users/adrian/projects/streams/plots/paper1/ps_distance.pdf}
\caption{Phase space distance ($D_{\rm ps}$) for 10 randomly selected stars integrated backwards in the correct potential (top) and a potential where $q_z$ is 25\% larger (bottom). The same 10 particles are used in both figures, so the initial conditions are identical. Red (thick, solid line) shows the galactocentric distance of the progenitor (in arbitrary, normalized units) over the integration. Horizontal (dashed) line shows $D_{\rm ps}=\sqrt{2}$.}\label{fig:ps_distance}
\end{center}
\end{figure}
